### 2018-01-18 Paper/jaccardbaetica.tex
update method

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mostly in handles but rarely in rims and body.  
The meaning of stamp is still under debate. Some authors suggest that they were identified as the owner of the olive land. Other authors propose that stamp could be the owner of the amphorae workshop.

@@

@@

We analysed a dataset of 131 stamps from 81 workshops. All the dataset was collected from CEIPAC database (citar). The workshops were located in different locations in Baetica province, along the river Guadalquivir and its tributary Genil.

@@

The dataset was analysed using a statistic method as Jaccard index. Jaccard distance was used to calculate the distance among different stamps.

>>>>

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mostly in handles but rarely in rims and body.  
The meaning of stamp is still under debate. Some authors suggest that they were identified as the owner of the olive land \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owner of the amphorae workshop. In any case, the use of these stamps defined the system of working in the workshops.

@@

%habría que citar a Dressel

@@

We analysed a dataset of 131 stamps from 81 workshops. All the dataset was collected from CEIPAC database (citar). The workshops were located in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology detected in the workshop is widely diverse from I-III B.C. However, all the workshops presented a long activity of production being difficult to specify a accurate chronology.

%hablar de la cronologia

@@

The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the similarity between sets. In our case, Jaccard distance was used to calculate the mutual presence of traits in the stamps.

%should i include morisita o horn

\subsection{Dissimilarity}

This method is used to measure the overlap between different samples of sets. 
%hablar sobre Horn (Morisita)

\bibliography{bibliotex}
